|

### 2022-09-01 paper_comparison/paper_comparison/paper_comparison.Rmd
clean up code

```{r get-third-result}
if (!file.exists(here::here("data/third_study/polynomials_lineup.rds"))) {
  polynomials_lineup <- get_polynomials_lineup()
  saveRDS(polynomials_lineup, here::here("data/third_study/polynomials_lineup.rds"))
} else {
  polynomials_lineup <- readRDS(here::here("data/third_study/polynomials_lineup.rds"))
}
```

@@

Residuals might be plotted, as a histogram or quantile-quantile plot to examine the distribution. Using classical linear regression model as an example, if the distribution is symmetric and unimodal, then it is well-behaved. But if the distribution is skewed, bimodal, multimodal, or even contains outliers, there is cause for concern. It is also possible to conduct a goodness of fit test to examine the distribution of residuals, such as Shapiro-Wilk Normality test [@shapiro1965analysis].

To examine the relationship between residuals, predicted values and each of the explanatory variables, it is recommend to plot them on a scatter plot with residuals on the y-axis. This type of plot is usually called residual plot. In general, one will check whether there is any noticeable pattern to determine if the model is well-behaved. However, it is a very difficult task for a human judge, though to make a decision that there's nothing there. It is especially common, particularly among new data analysts to report patterns when an experienced data analyst might quickly conclude that there are none. Generally, one looks for departures from nothingness like nonlinear dependency or heteroskedasticity. It is also possible to conduct a hypothesis test for non-linear dependence [@ramsey_tests_1969], and also use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

@@

>>>>

```{r get-lineup-data}
if (!file.exists(here::here("data/third_study/polynomials_lineup.rds"))) {
  polynomials_lineup <- get_polynomials_lineup()
  saveRDS(polynomials_lineup, here::here("data/third_study/polynomials_lineup.rds"))
} else {
  polynomials_lineup <- readRDS(here::here("data/third_study/polynomials_lineup.rds"))
}

if (!file.exists(here::here("data/fourth_study/heter_lineup.rds"))) {
  heter_lineup <- get_polynomials_lineup()
  saveRDS(heter_lineup, here::here("data/fourth_study/heter_lineup.rds"))
} else {
  heter_lineup <- readRDS(here::here("data/fourth_study/heter_lineup.rds"))
}
```

@@

Residuals might be plotted, as a histogram or quantile-quantile plot to examine the distribution. Using the classical linear regression model as an example, if the distribution is symmetric and unimodal, it is well-behaved. But if the distribution is skewed, bimodal, multimodal, or even contains outliers, there is cause for concern. Conducting a goodness of fit test is an alternative method for inspecting the distribution, such as the Shapiro-Wilk Normality test [@shapiro1965analysis].

To scrutinize the relationship between residuals, predicted values and each of the explanatory variables, it is recommend to plot them on a scatter plot. In general, one will check whether there is any noticeable pattern to determine if the model is well-behaved. However, it is a very difficult task for a human judge, though to make a decision that there's nothing there. It is especially common, particularly among new data analysts to report patterns when an experienced data analyst might quickly conclude that there are none. Generally, one looks for departures from nothingness like nonlinear dependency or heteroskedasticity. It is also possible to conduct a hypothesis test for non-linear dependence [@ramsey_tests_1969], and also use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

<!-- todo: check the two way interaction for x_dist and a -->

@@

```{r}
heter_conv_test_plot() %>%
  add_heter_SW_plot_layers() %>%
  add_heter_visual_test_plot_layers() +
  facet_grid(x_dist~a)
```
